Data Analysis and Modeling

### 2018-05-30 scripts/1_str_preprocessing.Rmd
Add imputation of likely bookings

---
title: "Pre Processing of the Short Term Data"
subtitle:  "For the 'To Airbnb' paper"
author: "Andy Krause and Gideon Aschwanden"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Pre Processing of the Short Term Data"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
---

### 2018-05-30 scripts/2_ltr_preprocessing.Rmd
Add imputation of likely bookings

---
title: "Pre Processing of the Long Term Data"
author: "Andy Krause and Gideon Aschwanden"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Pre Processing of the Long Term Data"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
---

### 2018-05-30 scripts/3_data_prep.Rmd
Add imputation of likely bookings

---
title: "Data Preparation, Integration and Cleaning"
output:
  htlm_document: default
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Data Preparation, Integration and Cleaning"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
---

### 2018-05-30 scripts/4_data_analysis.Rmd
Add imputation of likely bookings

---
title: "Should I Airbnb My Property: Analytic Code Explanation"
author: "Andy Krause and Gideon Aschwanden"
date: "March 10, 2017"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

This document describes all of the code used to the generate the output included in the 'Should I Airbnb my Property' study.  Additional analysis that were not included in the final report are also found within this document.  This analysis uses the output from the **3_data_prep.rmd** file found in the same online repository.

@@

@@

  exch_rate <- 1.32

  decision_date <- lubridate::as_date('2015-09-01')

@@

@@

  load(file.path(data_path, 'prepared', 'prepared_data.RData'))

@@

We begin the analysis by calculating the net revenues for the short term data.  We calculate three types of net revenues, Observed, Extrapolated (Actual) and Potential. The difference are described more fully in the writeup.

Before we start, we estimate two figures necessary to determine utility costs: 1) Costs per person per day (cpppd) and the average number of guests per bedroom.The State of Victoria gives energy costs at \$330 (apartment) to \$520 (house).  For 2 persons in an apartment that works out to \$5 per person per day.  For a house of 4 persons that works out to about \$4 per person per day. We use a mid point value of \$4.50 per person per day.  We use an estimate of 1.5 persons per bedroom in each unit.

@@

@@

@@

@@

  # Calculate likely revenue
  str_tdf$lik_revenue <- ((str_tdf$bookings * str_tdf$extr_par * str_tdf$med_rate) -
                           (str_tdf$bookings * str_tdf$avg_guests *
                             cpppd * str_tdf$extr_par))
```

@@

  str_tdf$pot_occ_rate <- ((str_tdf$bookings * str_tdf$extr_par) /
                             (366 - (366 * str_tdf$block_rate)))

>>>>

---
title: "Data Analysis and Modeling"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

This document describes all of the code used to the generate the output included in the 'To Airbnb?' study. This analysis uses the output from the **3_data_prep.rmd** file found in the same online repository.

@@

```{r set_options, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

@@

  # Exchange rate: AUS to US 
  exch_rate <- 1.32

  # Date of investment decision
  decision_date <- lubridate::as_date('2015-09-01')

@@

We then load the data.

@@

  load(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData'))

@@

We begin the analysis by calculating the net revenues for the short term data.  We calculate three types of net revenues, Actual, Likely (Extrapolated) and Potential. The differences are described more fully in the writeup.

Before we start, we estimate two figures necessary to determine utility costs: 1) Costs per person per day (cpppd) and the average number of guests per bedroom. The State of Victoria gives energy costs at \$330 (apartment) to \$520 (house).  For 2 persons in an apartment that works out to \$5 per person per day.  For a house of 4 persons that works out to about \$4 per person per day. We use a mid point value of \$4.50 per person per day.  We use an estimate of 1.5 persons per bedroom in each unit.

@@

We then calculate the actual net revenue by multiplying booking times median rate - utility costs.

@@

Next we create Likely Revenue, by imputing occupancy rates and revenues for the remainder of the year for those properties

@@

  # Create daily rate summary
  rate_summ <- str_tdf %>% 
   dplyr::select(property_id, daily_data) %>%
    tidyr::unnest() %>%
    dplyr::filter(status != 'B') %>%
    dplyr::group_by(date) %>%
    summarize(rate = length(which(status == 'R')) / n(),
            obs = n())

  # Create new cluster
  abb_cl <- get_default_cluster()

  # Register function and variable
  cluster_copy(abb_cl, impLikelyBookings)
  cluster_copy(abb_cl, rate_summ)
  cluster_library(abb_cl, c("magrittr", 'dplyr', 'tidyr'))

  # Summarize daily by property
  lik_book_df <- str_tdf %>%
    dplyr::filter(total_days != 366) %>%
    multidplyr::partition(property_id, cluster=abb_cl) %>% 
    dplyr::do(impLikelyBookings(., std=g)) %>% 
    dplyr::collect()

  # Add to the existing data
  str_tdf <- str_tdf %>%
    left_join(lik_book_df, by='property_id') %>%
    dplyr::mutate(lik_bookings = if_else(is.na(lik_bookings), bookings, as.integer(lik_bookings)))

  # Calculate likely revenue
  str_tdf$lik_revenue <- ((str_tdf$lik_bookings * str_tdf$med_rate) -
                           (str_tdf$lik_bookings * str_tdf$avg_guests * cpppd))

@@

@@

  str_tdf$pot_occ_rate <- ((str_tdf$lik_bookings) / (366 - (366 * str_tdf$block_rate)))
